---
title: "Result"
author: "Yicheng Shen"
date: "2023-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, cache = F, error = F, warning = F, eval = T, message = F)
library(metafor)
library(tidyverse)
library(kableExtra)
library(latex2exp)
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(out.width = "100%", fig.align = 'center')
```



# Story 1
```{r}
load("NMA Power Sim/df_indirect_BNMA_bias2.RData")
df_indirect_bias0.1 = df_indirect_bias[which(df_indirect_bias$pi_a==0.1),]
df_indirect_bias0.5 = df_indirect_bias[which(df_indirect_bias$pi_a==0.5),]

load("NMA Power Sim/df_indirect_BNMA_bias_2_additional2.RData")
df_indirect_bias_additional2_0.1 = df_indirect_bias_additional2[which(df_indirect_bias_additional2$pi_a==0.1),]
df_indirect_bias_additional2_0.5 = df_indirect_bias_additional2[which(df_indirect_bias_additional2$pi_a==0.5),]

df_indirect_bias0.1 = rbind(df_indirect_bias0.1, df_indirect_bias_additional2_0.1)
df_indirect_bias0.5 = rbind(df_indirect_bias0.5, df_indirect_bias_additional2_0.5)


load("NMA Power Sim/df_direct_BNMA_bias2.RData")
df_direct_bias0.1 = df_direct_bias[which(df_direct_bias$pi_a==0.1),] 
df_direct_bias0.5 = df_direct_bias[which(df_direct_bias$pi_a==0.5),]

load("NMA Power Sim/df_overall_BNMA_bias2.RData")
df_BNMA_bias0.1 = df_BNMA_bias[which(df_BNMA_bias$pi_a==0.1),]
df_BNMA_bias0.5 = df_BNMA_bias[which(df_BNMA_bias$pi_a==0.5),]


load("NMA Power Sim/df_overall_BNMA_bias2_additional.RData")
df_BNMA_bias_additional0.1 = df_BNMA_bias_additional[which(df_BNMA_bias_additional$pi_a==0.1),]
df_BNMA_bias_additional0.5 = df_BNMA_bias_additional[which(df_BNMA_bias_additional$pi_a==0.5),]

df_BNMA_bias0.1 = rbind(df_BNMA_bias0.1, df_BNMA_bias_additional0.1)
df_BNMA_bias0.5 = rbind(df_BNMA_bias0.5, df_BNMA_bias_additional0.5)


# Replace values in the tau variable with specified strings
df_indirect_bias0.5 <- df_indirect_bias0.5 %>%
  mutate(tau = case_when(
    tau == 0.001 ~ "τ = 0.001",
    tau == 0.2 ~ "τ = 0.2",
    tau == 0.4 ~ "τ = 0.4",
    TRUE ~ as.character(tau) # Handles any other values; adjust as necessary
  ))

df_direct_bias0.5 <- df_direct_bias0.5 %>%
  mutate(tau = case_when(
    tau == 0.001 ~ "τ = 0.001",
    tau == 0.2 ~ "τ = 0.2",
    tau == 0.4 ~ "τ = 0.4",
    TRUE ~ as.character(tau) # Handles any other values; adjust as necessary
  ))

df_BNMA_bias0.5 <- df_BNMA_bias0.5 %>%
  mutate(tau = case_when(
    tau == 0.001 ~ "τ = 0.001",
    tau == 0.2 ~ "τ = 0.2",
    tau == 0.4 ~ "τ = 0.4",
    TRUE ~ as.character(tau) # Handles any other values; adjust as necessary
  ))
```


```{r}
# df_indirect_bias_example = df_indirect_bias %>% filter(k_ab == 12)
# 
# pre0 = df_indirect_bias_example[1:9]
# pre0$k_ab = 1; pre0$k_ac = 1
# 
# pre1 = df_indirect_bias0.5[1:9]
# pre1$k_ab = 2; pre1$k_ac = 2
# 
# pre2 = df_indirect_bias0.5[1:9]
# pre2$k_ab = 3; pre2$k_ac = 3
# 
# df_indirect_bias_newpre = rbind(pre0, pre1, pre2)
```




```{r, fig.width=8, fig.height=4, error = F}
df_direct_bias0.5 %>% filter(pi_a == 0.5, k_bc < 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) + 
  geom_point(size = 2) + facet_wrap(~tau) + 
  labs(title = TeX("Direct Evidence Only (1 $\\leq k_{BC} \\leq$ 6) v.s Indirect Evidence Only ($k_{AB} = k_{AC} = 6)"), color = TeX("True: $OR_{BC}$"), x = TeX("Number of Studies"), y = "Power") + 
  scale_x_continuous(breaks = seq(1, 12, 1), labels = as.character(seq(1, 12, 1))) + 
  geom_hline(linetype = "dashed", data = df_indirect_bias0.5[which(df_indirect_bias0.5$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + ylim(0,1)


df_direct_bias0.5 %>% filter(pi_a == 0.5, k_bc <= 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) + 
  geom_point(size = 2) + facet_wrap(~tau) + 
  labs(title = TeX("Direct Evidence (1 $\\leq k_{BC} \\leq$ 12) v.s Indirect Evidence (1 $\\leq k_{AB} \\leq$ 12 & 1 $\\leq k_{AC} \\leq$ 12))"), color = TeX("True: $OR_{BC}$"), x = TeX("Number of Studies"), y = "Power") + 
  scale_x_continuous(breaks = seq(1, 12, 1), labels = as.character(seq(1, 12, 1))) +
  # scale_x_continuous(breaks = c(1, 2, 3, 4, 6, 12), labels = as.character(c(1, 2, 3, 4, 6, 12))) + 
  geom_line(linetype = "dashed", data = df_indirect_bias0.5, aes(y = power, x = k_ab, color = factor(OR_bc))) + ylim(0,1)


df_BNMA_bias0.5 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Direct Evidence"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "F1", data = df_direct_bias0.5[which(df_direct_bias0.5$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)



df_BNMA_bias0.5_sub = df_BNMA_bias0.5 %>% filter(OR_bc == 1.33)
df_direct_bias0.5_sub = df_direct_bias0.5 %>% filter(OR_bc == 1.33)
df_indirect_bias0.5_sub = df_indirect_bias0.5 %>% filter(OR_bc == 1.33)


df_BNMA_bias0.5_sub %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + 
  labs(title = TeX("Complete NMA vs. Only Direct Evidence vs. Only Indirect Evidence"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  geom_line(linetype = "F1", data = df_direct_bias0.5_sub[which(df_direct_bias0.5_sub$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ 
  geom_line(linetype = "dashed", data = df_indirect_bias0.5_sub[which(df_indirect_bias0.5_sub$k_ab %in% c(1,2,3,4,6)),], aes(y = power, x = k_ab, color = factor(OR_bc))) +
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


df_BNMA_bias0.5_sub %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + 
  geom_line(size = 0.5, aes(linetype = "Complete NMA")) +
  geom_point(size = 2) +
  facet_wrap(~tau) + 
  labs(title = TeX("Complete NMA vs. Only Direct Evidence vs. Only Indirect Evidence"), 
       color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  geom_line(linetype = "F1", data = df_direct_bias0.5_sub[which(df_direct_bias0.5_sub$k_bc %in% c(1,2,3,4,6)),], 
            aes(y = power, x = k_bc, color = factor(OR_bc), linetype = "Direct NMA"))+ 
  geom_line(linetype = "dashed", data = df_indirect_bias0.5_sub[which(df_indirect_bias0.5_sub$k_ab %in% c(1,2,3,4,6)),], 
            aes(y = power, x = k_ab, color = factor(OR_bc), linetype = "Indirect NMA")) + 
  ylim(0,1)+ 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  ylim(0,1) +
  scale_linetype_manual(name = "Analysis Type", values = c("Complete NMA" = "solid", "Direct NMA" = "F1", "Indirect NMA" = "dashed"))
```

```{r, fig.width=10, fig.height=4}
df_BNMA_bias0.5 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + 
  geom_line(aes(linetype = "Complete NMA"), size = 0.5) +
  geom_point(size = 2) + facet_wrap(~tau) + 
  labs(title = TeX("Complete NMA (More Direct) vs. Only Direct Evidence vs. Only Indirect Evidence"), 
       color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  geom_line(data = df_direct_bias0.5[which(df_direct_bias0.5$k_bc %in% c(1,2,3,4,6)),], alpha = 0.75, aes(y = power, x = k_bc, linetype = "Direct Evidence", color = factor(OR_bc))) + 
  geom_line(data = df_indirect_bias0.5[which(df_indirect_bias0.5$k_ab %in% c(1,2,3,4,6)),], aalpha = 0.75, aes(y = power, x = k_ab, linetype = "Indirect Evidence", color = factor(OR_bc))) + 
  scale_linetype_manual(name = "Types of Evidence Cycle", values = c("solid","F1","dashed")) + 
    guides(linetype = guide_legend(keywidth = 2.5, keyheight = 0.1))  + 
  # scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  ylim(0,1) + scale_color_brewer(palette="Set1")


df_BNMA_bias0.5 %>% filter(k_bc == 2, k_ab < 12) %>% 
  ggplot(aes(x = k_ab, y = power, color = factor(OR_bc))) + 
  geom_line(aes(linetype = "Complete NMA"), size = 0.5) +
  geom_point(size = 2) + facet_wrap(~tau) + 
  labs(title = TeX("Complete NMA (More Indirect) vs. Only Direct Evidence vs. Only Indirect Evidence"), 
       color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  geom_line(data = df_direct_bias0.5[which(df_direct_bias0.5$k_bc %in% c(1,2,3,4,6)),], alpha = 0.75, aes(y = power, x = k_bc, linetype = "Direct Evidence", color = factor(OR_bc))) + 
  geom_line(data = df_indirect_bias0.5[which(df_indirect_bias0.5$k_ab %in% c(1,2,3,4,6)),], alpha = 0.75, aes(y = power, x = k_ab, linetype = "Indirect Evidence", color = factor(OR_bc))) + 
  scale_linetype_manual(name = "Types of Evidence Cycle", values = c("solid","F1","dashed")) + 
    guides(linetype = guide_legend(keywidth = 2.5, keyheight = 0.1))  + 
  # scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  ylim(0,1)+ scale_color_brewer(palette="Set1")


df_BNMA_bias0.5_sub = df_BNMA_bias0.5 %>% filter(OR_bc == 1.33)
df_direct_bias0.5_sub = df_direct_bias0.5 %>% filter(OR_bc == 1.33)
df_indirect_bias0.5_sub = df_indirect_bias0.5 %>% filter(OR_bc == 1.33)


df_BNMA_bias0.5_sub %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + 
  geom_line(aes(linetype = "Complete NMA"), size = 0.5) +
  geom_point(size = 2) +
  facet_wrap(~tau) + 
  labs(title = TeX("Complete NMA (More Direct) vs. Only Direct Evidence vs. Only Indirect Evidence"), 
       color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  geom_line(data = df_direct_bias0.5_sub[which(df_direct_bias0.5_sub$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, linetype = "Direct Evidence", color = factor(OR_bc))) + 
  geom_line(data = df_indirect_bias0.5_sub[which(df_indirect_bias0.5_sub$k_ab %in% c(1,2,3,4,6)),], aes(y = power, x = k_ab, linetype = "Indirect Evidence", color = factor(OR_bc))) + 
  scale_linetype_manual(name = "Types of Evidence Cycle", values = c("solid","F1","dashed")) + 
  guides(linetype = guide_legend(keywidth = 2.5, keyheight = 0.1))  + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  ylim(0,1)+ scale_color_brewer(palette="Set1")


df_BNMA_bias0.5_sub %>% filter(k_bc == 2, k_ab < 12) %>% 
  ggplot(aes(x = k_ab, y = power, color = factor(OR_bc))) + 
  geom_line(aes(linetype = "Complete NMA"), size = 0.5) +
  geom_point(size = 2) +
  facet_wrap(~tau) + 
  labs(title = TeX("Complete NMA (More Indirect) vs. Only Direct Evidence vs. Only Indirect Evidence"), 
       color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  geom_line(data = df_direct_bias0.5_sub[which(df_direct_bias0.5_sub$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, linetype = "Direct Evidence", color = factor(OR_bc))) + 
  geom_line(data = df_indirect_bias0.5_sub[which(df_indirect_bias0.5_sub$k_ab %in% c(1,2,3,4,6)),], aes(y = power, x = k_ab, linetype = "Indirect Evidence", color = factor(OR_bc))) + 
  scale_linetype_manual(name = "Types of Evidence Cycle", values = c("solid","F1","dashed")) + 
  guides(linetype = guide_legend(keywidth = 2.5, keyheight = 0.1))  + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  ylim(0,1) + scale_color_brewer(palette="Set1")
```


```{r, fig.width=10, fig.height=4}
load("NMA Power Sim/df_direct_BNMA_bias.RData")
df_direct_summ = df_direct_bias %>% group_by(pi_a, OR_bc, tau, k_bc) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            avg_bias = mean((point_est - point_true)), 
            avg_bias_abs = (mean(abs(point_est - point_true))))

df_direct_summ0.1 = df_direct_summ[which(df_direct_summ$pi_a==0.1),] 
df_direct_summ0.5 = df_direct_summ[which(df_direct_summ$pi_a==0.5),]


load("NMA Power Sim/df_indirect_BNMA_bias.RData")
df_indirect_summ = df_indirect_bias %>% group_by(pi_a, OR_bc, tau, k_ab, k_ac) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            avg_bias = mean((point_est - point_true)), 
            avg_bias_abs = (mean(abs(point_est - point_true))))

df_indirect_summ0.1 = df_indirect_summ[which(df_indirect_summ$pi_a==0.1),]
df_indirect_summ0.5 = df_indirect_summ[which(df_indirect_summ$pi_a==0.5),]

df_indirect_summ0.1 = rbind(df_indirect_summ0.1, df_indirect_bias_additional2_0.1)
df_indirect_summ0.5 = rbind(df_indirect_summ0.5, df_indirect_bias_additional2_0.5)


df_indirect_summ0.5 <- df_indirect_summ0.5 %>%
  mutate(tau = case_when(
    tau == 0.001 ~ "τ = 0.001",
    tau == 0.2 ~ "τ = 0.2",
    tau == 0.4 ~ "τ = 0.4",
    TRUE ~ as.character(tau) # Handles any other values; adjust as necessary
  ))

df_direct_summ0.5 <- df_direct_summ0.5 %>%
  mutate(tau = case_when(
    tau == 0.001 ~ "τ = 0.001",
    tau == 0.2 ~ "τ = 0.2",
    tau == 0.4 ~ "τ = 0.4",
    TRUE ~ as.character(tau) # Handles any other values; adjust as necessary
  ))



df_BNMA_bias0.5 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + 
  geom_line(aes(linetype = "Complete NMA"), size = 0.5) +
  geom_point(size = 2) +
  facet_wrap(~tau) + 
  labs(title = TeX("Complete NMA (More Direct) vs. Only Direct Evidence vs. Only Indirect Evidence"), 
       color = TeX("True $OR_{BC}$"), y = "Magnitude of Bias", x = "Number of Studies") + 
  geom_line(data = df_direct_summ0.5[which(df_direct_summ0.5$k_bc %in% c(1,2,3,4,6)),], aes(y = avg_bias_abs, x = k_bc, linetype = "Direct Evidence", color = factor(OR_bc))) + 
  geom_line(data = df_indirect_summ0.5[which(df_indirect_summ0.5$k_ab %in% c(1,2,3,4,6)),], aes(y = avg_bias_abs, x = k_ab, linetype = "Indirect Evidence", color = factor(OR_bc))) + 
  scale_linetype_manual(name = "Types of Evidence Cycle", values = c("solid","F1","dashed")) + 
  guides(linetype = guide_legend(keywidth = 2.5, keyheight = 0.1))  + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  ylim(0,0.6)  + scale_color_brewer(palette="Set1")


df_BNMA_bias0.5 %>% filter(k_bc == 2, k_ab < 12) %>% 
  ggplot(aes(x = k_ab, y = avg_bias_abs, color = factor(OR_bc))) + 
  geom_line(aes(linetype = "Complete NMA"), size = 0.5) +
  geom_point(size = 2) +
  facet_wrap(~tau) + 
  labs(title = TeX("Complete NMA (More Indirect) vs. Only Direct Evidence vs. Only Indirect Evidence"), 
       color = TeX("True $OR_{BC}$"), y = "Magnitude of Bias", x = "Number of Studies") + 
  geom_line(data = df_direct_summ0.5[which(df_direct_summ0.5$k_bc %in% c(1,2,3,4,6)),], aes(y = avg_bias_abs, x = k_bc, linetype = "Direct Evidence", color = factor(OR_bc))) + 
  geom_line(data = df_indirect_summ0.5[which(df_indirect_summ0.5$k_ab %in% c(1,2,3,4,6)),], aes(y = avg_bias_abs, x = k_ab, linetype = "Indirect Evidence", color = factor(OR_bc))) + 
  scale_linetype_manual(name = "Types of Evidence Cycle", values = c("solid","F1","dashed")) + 
  guides(linetype = guide_legend(keywidth = 2.5, keyheight = 0.1))  + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  ylim(0,0.6)  + scale_color_brewer(palette="Set1")
```











<!-- #################### -->

```{r, fig.width=12, fig.height=3, error = F}
# 1. 
indirect_p1 = df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)

indirect_p2 = df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)


grid.arrange(
  arrangeGrob(
    indirect_p1 + theme(legend.position = "none"),
    indirect_p2 + theme(legend.position = "none"),
    nrow = 1
  ),
  lemon::g_legend(
    indirect_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(10, 1)
)
```

```{r, fig.width=12, fig.height=3, error = F}
# 2. 
df_indirect_bias0.1 = df_indirect_bias[which(df_indirect_bias$pi_a==0.1),]
df_indirect_bias0.5 = df_indirect_bias[which(df_indirect_bias$pi_a==0.5),]

load("NMA Power Sim/df_direct_BNMA_bias2.RData")

df_direct_bias0.1 = df_direct_bias[which(df_direct_bias$pi_a==0.1),] 
df_direct_bias0.5 = df_direct_bias[which(df_direct_bias$pi_a==0.5),]

direct_p1 = df_direct_bias0.1 %>% filter(pi_a == 0.1, k_bc < 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) + 
  geom_point(size = 2) + facet_wrap(~tau) + 
  labs(title = TeX("Only Direct Evidence: $k_{BC}$ $\\in$ (1,2,3,6), $pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = TeX("Number of Studies"), y = "Power") + 
  scale_x_continuous(breaks = seq(1, 12, 1), labels = as.character(seq(1, 12, 1))) + 
  geom_hline(linetype = "dashed", data = df_indirect_bias0.1[which(df_indirect_bias0.1$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + ylim(0,1)

direct_p2 = df_direct_bias0.5 %>% filter(pi_a == 0.5, k_bc < 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) + 
  geom_point(size = 2) + facet_wrap(~tau) + 
  labs(title = TeX("Only Direct Evidence: $k_{BC}$ $\\in$ (1,2,3,6), $pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = TeX("Number of Studies"), y = "Power") + 
  scale_x_continuous(breaks = seq(1, 12, 1), labels = as.character(seq(1, 12, 1))) + 
  geom_hline(linetype = "dashed", data = df_indirect_bias0.1[which(df_indirect_bias0.1$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + ylim(0,1)

grid.arrange(
  arrangeGrob(
    direct_p1 + theme(legend.position = "none"),
    direct_p2 + theme(legend.position = "none"),
    nrow = 1
  ),
  lemon::g_legend(
    direct_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(10, 1)
)

```

```{r, fig.width=12, fig.height=3, error = F}
# 3. 
complete_p1 = df_BNMA_bias0.1 %>% filter(pi_a == 0.1, k_bc == 1) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
 labs(title = TeX("Complete NMA vs. Only Indirect Evidence, $pi_A = 0.1$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  geom_hline(linetype = "dashed", data = df_indirect_bias0.1[which(df_indirect_bias0.1$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + ylim(0,1)

complete_p2 = df_BNMA_bias0.5 %>% filter(pi_a == 0.5, k_bc == 1) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
 labs(title = TeX("Complete NMA vs. Only Indirect Evidence, $pi_A = 0.5$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  scale_x_continuous(breaks = seq(1, 12, 1), labels = as.character(seq(1, 12, 1))) + 
  geom_hline(linetype = "dashed", data = df_indirect_bias0.1[which(df_indirect_bias0.1$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + ylim(0,1) 


grid.arrange(
  arrangeGrob(
    complete_p1 + theme(legend.position = "none"),
    complete_p2 + theme(legend.position = "none"),
    nrow = 1
  ),
  lemon::g_legend(
    direct_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(10, 1)
)

```


```{r, fig.height=6, fig.width=12}
# 4.
overall_p1 <- df_BNMA_bias0.1 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Indirect Evidence, $pi_A = 0.1$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias0.1[which(df_indirect_bias0.1$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)

overall_p2 <- df_BNMA_bias0.5 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Indirect Evidence $pi_A = 0.5$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias0.5[which(df_indirect_bias0.5$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)


overall_p3 <- df_BNMA_bias0.1 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Direct Evidence, $pi_A = 0.1$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "F1", data = df_direct_bias0.1[which(df_direct_bias0.1$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)

overall_p4 <- df_BNMA_bias0.5 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Direct Evidence, $pi_A = 0.5$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "F1", data = df_direct_bias0.5[which(df_direct_bias0.5$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)



grid.arrange(
  arrangeGrob(
    overall_p1 + theme(legend.position = "none"),
    overall_p2 + theme(legend.position = "none"),
    overall_p3 + theme(legend.position = "none"),
    overall_p4 + theme(legend.position = "none"),
    nrow = 2
  ),
  lemon::g_legend(
    overall_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(10, 1)
)
```


```{r, fig.height=3, fig.width=12}
# 4.
overall_p1 <- df_BNMA_bias0.1 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Indirect Evidence, $pi_A = 0.1$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias0.1[which(df_indirect_bias0.1$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1) + geom_line(linetype = "F1", data = df_direct_bias0.1[which(df_direct_bias0.1$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))

overall_p2 <- df_BNMA_bias0.5 %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Indirect Evidence $pi_A = 0.5$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias0.5[which(df_indirect_bias0.5$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)  + geom_line(linetype = "F1", data = df_direct_bias0.5[which(df_direct_bias0.5$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))


# overall_p3 <- df_BNMA_bias0.1 %>% filter(k_ab == 6) %>% 
#   ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
#     geom_point(size = 2) +
#   facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Direct Evidence, $pi_A = 0.1$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_bias0.1[which(df_direct_bias0.1$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)
# 
# overall_p4 <- df_BNMA_bias0.5 %>% filter(k_ab == 6) %>% 
#   ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
#     geom_point(size = 2) +
#   facet_wrap(~tau) + labs(title = TeX("Complete NMA vs. Only Direct Evidence, $pi_A = 0.5$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_bias0.5[which(df_direct_bias0.5$k_bc %in% c(1,2,3,4,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)



grid.arrange(
  arrangeGrob(
    overall_p1 + theme(legend.position = "none"),
    overall_p2 + theme(legend.position = "none"),
    nrow = 1
  ),
  lemon::g_legend(
    overall_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(10, 1)
)


grid.arrange(
  arrangeGrob(
    overall_p3 + theme(legend.position = "none"),
    overall_p4 + theme(legend.position = "none"),
    nrow = 1
  ),
  lemon::g_legend(
    overall_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(10, 1)
)
```





```{r, fig.width=12, fig.height=3, error = F}
# 5. 
complete_p5 = df_BNMA_bias0.1 %>% filter(k_ab == 12, k_bc == 2) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.3, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
 labs(title = TeX("Complete NMA with Doubled Indirect Evidence, $pi_A = 0.1$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  geom_hline(linetype = "dashed", data = df_BNMA_bias0.1 %>% filter(k_ab == 6, k_bc == 1), aes(yintercept = power, color = factor(OR_bc))) + ylim(0,1)

complete_p6 = df_BNMA_bias0.5 %>% filter(k_ab == 12, k_bc == 2)  %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.3, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
 labs(title = TeX("Complete NMA with Doubled Indirect Evidence, $pi_A = 0.5$"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + 
  scale_x_continuous(breaks = seq(1, 12, 1), labels = as.character(seq(1, 12, 1))) + 
  geom_hline(linetype = "dashed", data = df_BNMA_bias0.5 %>% filter(k_ab == 6, k_bc == 1), aes(yintercept = power, color = factor(OR_bc))) + ylim(0,1) 


grid.arrange(
  arrangeGrob(
    complete_p5 + theme(legend.position = "none"),
    complete_p6 + theme(legend.position = "none"),
    nrow = 1
  ),
  lemon::g_legend(
    direct_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(10, 1)
)

```

```{r, fig.width=12, fig.height=15, error = F}

png('result.png', width = 800, height = 1200)

grid.arrange(
  arrangeGrob(
    indirect_p1 + theme(legend.position = "none"), indirect_p2 + theme(legend.position = "none"),
    direct_p1 + theme(legend.position = "none"), direct_p2 + theme(legend.position = "none"),
    complete_p1 + theme(legend.position = "none") + theme(legend.position = "none") + labs( x = ""), complete_p2 + theme(legend.position = "none") + labs( x = ""),
    overall_p3 + theme(legend.position = "none"), overall_p4 + theme(legend.position = "none"),
    complete_p5 + theme(legend.position = "none") + theme(legend.position = "none") + labs( x = ""), complete_p6 + theme(legend.position = "none") + theme(legend.position = "none") + labs( x = ""),
    nrow = 5 
  ),
  lemon::g_legend(
    indirect_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(20, 1)
)

dev.off()
```




# Story 2

```{r, fig.width=12, fig.height=12, error = F}
load("NMA Power Sim/df_indirect_BNMA_bias_2_additional.RData")

png('result2.png', width = 1200, height = 1200)

# 1. 
indirect_p1 = df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)

indirect_p2 = df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)


indirect_p3 = df_indirect_bias_additional %>% filter(k_ab == 6, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = 6, k_{AC} = 12, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)

indirect_p4 = df_indirect_bias_additional %>% filter(k_ab == 6, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = 6, k_{AC} = 12, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)


indirect_p5 = df_indirect_bias_additional %>% filter(k_ab == 12, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = 12, k_{AC} = 6, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)

indirect_p6 = df_indirect_bias_additional %>% filter(k_ab == 12, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = 12, k_{AC} = 6, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)


indirect_p7 = df_indirect_bias %>% filter(k_ab == 12, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)

indirect_p8 = df_indirect_bias %>% filter(k_ab == 12, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.5, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("Only Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)



grid.arrange(
  arrangeGrob(
    indirect_p1 + theme(legend.position = "none"),
    indirect_p2 + theme(legend.position = "none"),
    indirect_p3 + theme(legend.position = "none"),
    indirect_p4 + theme(legend.position = "none"),
    indirect_p5 + theme(legend.position = "none"),
    indirect_p6 + theme(legend.position = "none"),
    indirect_p7 + theme(legend.position = "none"),
    indirect_p8 + theme(legend.position = "none"),
    nrow = 4
  ),
  lemon::g_legend(
    indirect_p1 + theme(legend.position = "bottom") + guides(colour = guide_legend(nrow = 1))
  ),
  nrow = 2,
  heights = c(25, 1)
)

dev.off()
```







# Part 1: Simulation of power / correct ranking probability
## Indirect Evidence, Power -- LARE

```{r, fig.height=5.5, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias2.RData")
load("NMA Power Sim/df_direct_BNMA_bias2.RData")
load("NMA Power Sim/df_overall_BNMA_bias2.RData")

gridExtra::grid.arrange(

df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)
,
df_indirect_bias %>% filter(k_ab == 12, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power") + ylim(0,1)

,

df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)
,
df_indirect_bias %>% filter(k_ab == 12, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power") + ylim(0,1)
)
```

# Indirect Evidence, Probability of Correct Ranking Order -- LARE

```{r, fig.height=5.5, fig.width=12}
# ranking correct in indirect evidence

gridExtra::grid.arrange(

df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = rank_correct, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = rank_correct, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Probability of Correct Ranking")  + ylim(0.5,1)
,
df_indirect_bias %>% filter(k_ab == 12, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = rank_correct, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = rank_correct, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Probability of Correct Ranking") + ylim(0.5,1)

,

df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = rank_correct, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = rank_correct, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Probability of Correct Ranking")  + ylim(0.5,1)
,
df_indirect_bias %>% filter(k_ab == 12, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = rank_correct, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = rank_correct, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Probability of Correct Ranking") + ylim(0.5,1)
)
```

# Direct Evidence, Power -- GEMTC (LARE)

```{r, fig.height=5.5, fig.width=12}
### Power Direct

gridExtra::grid.arrange(

df_direct_bias %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) + 
  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.1", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + ylim(0,1)

,
df_direct_bias %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(2,4,6,12), pi_a = 0.1", color = "True OR_bc") +
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)

,

df_direct_bias %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)

,
df_direct_bias %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  geom_point(size = 2) + 
  facet_wrap(~tau) + labs(title = "Direct Evi:  k_bc in c(2,4,6,12), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)
)

```


# Direct Evidence, Probability of Correct Ranking Order
## GEMTC (LARE)
```{r, fig.height=5.5, fig.width=12}
### Rank Correct Direct

gridExtra::grid.arrange(

df_direct_bias %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.1", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + ylim(0.5,1)

,
df_direct_bias %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(2,4,6,12), pi_a = 0.1", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + ylim(0.5,1)

,

df_direct_bias %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + ylim(0.5,1)

,
df_direct_bias %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Direct Evi:  k_bc in c(2,4,6,12), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + ylim(0.5,1)
)
```


# Overall evidence powers in comparison, with pi_a=0.1 -- LARE

```{r, fig.height=5.5, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias2.RData")
load("NMA Power Sim/df_direct_BNMA_bias2.RData")
load("NMA Power Sim/df_overall_BNMA_bias2.RData")

df_indirect_bias = df_indirect_bias[which(df_indirect_bias$pi_a==0.1),]
df_direct_bias = df_direct_bias[which(df_direct_bias$pi_a==0.1),]
df_BNMA_bias =  df_BNMA_bias[which(df_BNMA_bias$pi_a==0.1),]

a <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 6)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias[which(df_indirect_bias$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

b <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias[which(df_indirect_bias$k_ab==12),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


c <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Overall vs. Only Direct Evidence ($k_{BC}$ = 1, 2, 3, 6)"), color = TeX("True $OR_{BC}$"),  y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_bias[which(df_direct_bias$k_bc %in% c(1,2,3,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

d <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Overall vs. Only Direct Evidence ($k_{BC}$ = 2, 4, 6, 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_bias[which(df_direct_bias$k_bc %in% c(2,4,6,12)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)

gridExtra::grid.arrange(a,b,c,d,ncol = 2)

```

# Overall evidence powers in comparison, with pi_a=0.5 -- LARE

```{r, fig.height=5.5, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias2.RData")
load("NMA Power Sim/df_direct_BNMA_bias2.RData")
load("NMA Power Sim/df_overall_BNMA_bias2.RData")

df_indirect_bias = df_indirect_bias[which(df_indirect_bias$pi_a==0.5),]
df_direct_bias = df_direct_bias[which(df_direct_bias$pi_a==0.5),]
df_BNMA_bias =  df_BNMA_bias[which(df_BNMA_bias$pi_a==0.5),]

a <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Indirect (k_ab = k_ac = 6)", color = "True OR_bc") + theme_bw() + geom_hline(linetype = "dashed", data = df_indirect_bias[which(df_indirect_bias$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

b <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Indirect (k_ab = k_ac = 12)", color = "True OR_bc") + theme_bw()  + geom_hline(linetype = "dashed", data = df_indirect_bias[which(df_indirect_bias$k_ab==12),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


c <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Direct (k_bc = 1, 2, 3, 6)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_bias[which(df_direct_bias$k_bc %in% c(1,2,3,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

d <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Direct (k_bc = 2, 4, 6, 12)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_bias[which(df_direct_bias$k_bc %in% c(2,4,6,12)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)

gridExtra::grid.arrange(a,b,c,d,ncol = 2)
```


# Part 2: Absolute average bias (magnitude of bias)


```{r, fig.height=5.5, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias.RData")
load("NMA Power Sim/df_direct_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias3.RData")

df_indirect_summ = df_indirect_bias %>% group_by(pi_a, OR_bc, tau, k_ab, k_ac) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))

df_direct_summ = df_direct_bias %>% group_by(pi_a, OR_bc, tau, k_bc) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))

# df_BNMA_summ = df_BNMA_bias %>% group_by(pi_a, OR_bc, tau, k_ab, k_ac, k_bc) %>%
#    summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
#              bias_avg = (mean(point_est - point_true)))


gridExtra::grid.arrange(

df_indirect_summ %>% filter(k_ab == 6, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = bias_avg, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = bias_avg, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Bias")  + 
  # ylim(-0.05,0.05) + 
  geom_hline(yintercept = 0)
,
df_indirect_summ %>% filter(k_ab == 12, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = bias_avg, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = bias_avg, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Bias")  + 
  # ylim(-0.05,0.05) + 
  geom_hline(yintercept = 0)

,

df_indirect_summ %>% filter(k_ab == 6, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = bias_avg, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = bias_avg, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Bias")  + 
  # ylim(-0.05,0.05) + 
  geom_hline(yintercept = 0)
,
df_indirect_summ %>% filter(k_ab == 12, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = bias_avg, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = bias_avg, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Bias")   + 
  # ylim(-0.05,0.05) + 
  geom_hline(yintercept = 0)
)


gridExtra::grid.arrange(

df_direct_summ %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = bias_avg, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.1", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + 
  # ylim(-0.05,0.05) + 
  geom_hline(yintercept = 0)

,
df_direct_summ %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = bias_avg, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(2,4,6,12), pi_a = 0.1", color = "True OR_bc") +
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  # ylim(-0.05,0.05) + 
  geom_hline(yintercept = 0)

,

df_direct_summ %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = bias_avg, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + 
  # ylim(-0.05,0.05) + 
  geom_hline(yintercept = 0)

,
df_direct_summ %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = bias_avg, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Direct Evi:  k_bc in c(2,4,6,12), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + 
  # ylim(-0.05,0.05) + 
  geom_hline(yintercept = 0)
)
```

## Absolute bias of overall evidence in comparison, pi_a = 0.1

```{r, fig.height=5.5, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias.RData")
load("NMA Power Sim/df_direct_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias3.RData")

df_indirect_summ = df_indirect_bias %>% group_by(pi_a, OR_bc, tau, k_ab, k_ac) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))

df_direct_summ = df_direct_bias %>% group_by(pi_a, OR_bc, tau, k_bc) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))



df_indirect_summ = df_indirect_summ[which(df_indirect_summ$pi_a==0.1),]
df_direct_summ = df_direct_summ[which(df_direct_summ$pi_a==0.1),]
df_BNMA_bias =  df_BNMA_bias[which(df_BNMA_bias$pi_a==0.1),]

a <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Indirect (k_ab = k_ac = 6)", color = "True OR_bc") + theme_bw() + geom_hline(linetype = "dashed", data = df_indirect_summ[which(df_indirect_summ$k_ab==6),], aes(yintercept = bias_avg, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

b <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Indirect (k_ab = k_ac = 12)", color = "True OR_bc") + theme_bw()  + geom_hline(linetype = "dashed", data = df_indirect_summ[which(df_indirect_summ$k_ab==12),], aes(yintercept = bias_avg, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0) 


c <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Direct (k_bc = 1, 2, 3, 6)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_summ[which(df_direct_summ$k_bc %in% c(1,2,3,6)),], aes(y = bias_avg, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

d <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Direct (k_bc = 2, 4, 6, 12)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_summ[which(df_direct_summ$k_bc %in% c(2,4,6,12)),], aes(y = bias_avg, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0)

gridExtra::grid.arrange(a,b,c,d,ncol = 2)
```

## Absolute bias of overall evidence in comparison, pi_a = 0.5

```{r, fig.height=5.5, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias.RData")
load("NMA Power Sim/df_direct_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias2.RData")

df_indirect_summ = df_indirect_bias %>% group_by(pi_a, OR_bc, tau, k_ab, k_ac) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))

df_direct_summ = df_direct_bias %>% group_by(pi_a, OR_bc, tau, k_bc) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))


df_indirect_summ = df_indirect_summ[which(df_indirect_summ$pi_a==0.5),]
df_direct_summ = df_direct_summ[which(df_direct_summ$pi_a==0.5),]
df_BNMA_bias =  df_BNMA_bias[which(df_BNMA_bias$pi_a==0.5),]

a <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Indirect (k_ab = k_ac = 6)", color = "True OR_bc") + theme_bw() + geom_hline(linetype = "dashed", data = df_indirect_summ[which(df_indirect_summ$k_ab==6),], aes(yintercept = bias_avg, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

b <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Indirect (k_ab = k_ac = 12)", color = "True OR_bc") + theme_bw()  + geom_hline(linetype = "dashed", data = df_indirect_summ[which(df_indirect_summ$k_ab==12),], aes(yintercept = bias_avg, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0) 


c <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Direct (k_bc = 1, 2, 3, 6)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_summ[which(df_direct_summ$k_bc %in% c(1,2,3,6)),], aes(y = bias_avg, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

d <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "Overall vs. Only Direct (k_bc = 2, 4, 6, 12)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_summ[which(df_direct_summ$k_bc %in% c(2,4,6,12)),], aes(y = bias_avg, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0)

gridExtra::grid.arrange(a,b,c,d,ncol = 2)
```


# Part 3: LARE vs ABRE 
# Indirect Evidence, Power 

```{r, fig.height=11, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias2.RData")
load("NMA Power Sim/df_direct_BNMA_bias2.RData")
load("NMA Power Sim/df_overall_BNMA_bias2.RData")
load("Arm-based Sim/df_indirect_BNMA_AB_bias.RData")
load("Arm-based Sim/df_direct_BNMA_AB_bias.RData")
load("Arm-based Sim/df_overall_BNMA_AB_bias.RData")

gridExtra::grid.arrange(

df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("LARE: Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)
,

df_indirect_new %>% filter(k_ab == 6, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power") + ylim(0,1)
,

df_indirect_bias %>% filter(k_ab == 12, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + 
  labs(title = TeX("LARE: Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power") + ylim(0,1)
,

df_indirect_new %>% filter(k_ab == 12, pi_a == 0.1) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.1$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power") + ylim(0,1)
,

df_indirect_bias %>% filter(k_ab == 6, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("LARE: Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1),

df_indirect_new %>% filter(k_ab == 6, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Indirect Evidence: $k_{AB} = k_{AC} = 6, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power")  + ylim(0,1)
,

df_indirect_bias %>% filter(k_ab == 12, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + 
  geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) +
  labs(title = TeX("LARE: Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power") + ylim(0,1)
,

df_indirect_new %>% filter(k_ab == 12, pi_a == 0.5) %>% 
  ggplot(aes(x = k_ac, y = power, color = factor(OR_bc)))  + geom_hline(size = 1.2, aes(yintercept = power, color = factor(OR_bc))) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Indirect Evidence: $k_{AB} = k_{AC} = 12, pi_A = 0.5$"), color = TeX("True: $OR_{BC}$"), x = "", y = "Power") + ylim(0,1)

,nrow = 4
)
```



# Direct Evidence, Power -- LARE vs ABRE

```{r, fig.height=11, fig.width=12}
### Power Direct

gridExtra::grid.arrange(

df_direct_bias %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.1", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + ylim(0,1)
,
df_direct_new %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.1", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + ylim(0,1)
,


df_direct_bias %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Direct Evi: k_bc in c(2,4,6,12), pi_a = 0.1", color = "True OR_bc") +
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)
,
df_direct_new %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.1) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Direct Evi: k_bc in c(2,4,6,12), pi_a = 0.1", color = "True OR_bc") +
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)
,


df_direct_bias %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
,
df_direct_new %>% filter(k_bc %in% c(1,2,3,6), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Direct Evi: k_bc in c(1,2,3,6), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
,


df_direct_bias %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Direct Evi:  k_bc in c(2,4,6,12), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)
,
df_direct_new %>% filter(k_bc %in% c(2,4,6,12), pi_a == 0.5) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
    geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Direct Evi:  k_bc in c(2,4,6,12), pi_a = 0.5", color = "True OR_bc") + 
  scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)
,

nrow = 4
)
```


# Overall evidence powers in comparison, with pi_a=0.1 -- LARE

```{r, fig.height=11, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias2.RData")
load("NMA Power Sim/df_direct_BNMA_bias2.RData")
load("NMA Power Sim/df_overall_BNMA_bias2.RData")
load("Arm-based Sim/df_indirect_BNMA_AB_bias.RData")
load("Arm-based Sim/df_direct_BNMA_AB_bias.RData")
load("Arm-based Sim/df_overall_BNMA_AB_bias.RData")

df_indirect_bias = df_indirect_bias[which(df_indirect_bias$pi_a==0.1),]
df_direct_bias = df_direct_bias[which(df_direct_bias$pi_a==0.1),]
df_BNMA_bias =  df_BNMA_bias[which(df_BNMA_bias$pi_a==0.1),]
df_indirect_new = df_indirect_new[which(df_indirect_new$pi_a==0.1),]
df_direct_new = df_direct_new[which(df_direct_new$pi_a==0.1),]
df_BNMA_new =  df_BNMA_new[which(df_BNMA_new$pi_a==0.1),]

a <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 6)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias[which(df_indirect_bias$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

b <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias[which(df_indirect_bias$k_ab==12),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


c <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Direct Evidence ($k_{BC}$ = 1, 2, 3, 6)"), color = TeX("True $OR_{BC}$"),  y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_bias[which(df_direct_bias$k_bc %in% c(1,2,3,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

d <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Direct Evidence ($k_{BC}$ = 2, 4, 6, 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_bias[which(df_direct_bias$k_bc %in% c(2,4,6,12)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


a1 <- df_BNMA_new %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 6)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_new[which(df_indirect_new$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

b1 <- df_BNMA_new %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_new[which(df_indirect_new$k_ab==12),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


c1 <- df_BNMA_new %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Direct Evidence ($k_{BC}$ = 1, 2, 3, 6)"), color = TeX("True $OR_{BC}$"),  y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_new[which(df_direct_new$k_bc %in% c(1,2,3,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

d1 <- df_BNMA_new %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Direct Evidence ($k_{BC}$ = 2, 4, 6, 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_new[which(df_direct_new$k_bc %in% c(2,4,6,12)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


gridExtra::grid.arrange(a,a1, b,b1, c,c1, d,d1, nrow = 4)

```

# Overall evidence powers in comparison, with pi_a=0.5 -- LARE
```{r, fig.height=11, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias2.RData")
load("NMA Power Sim/df_direct_BNMA_bias2.RData")
load("NMA Power Sim/df_overall_BNMA_bias2.RData")
load("Arm-based Sim/df_indirect_BNMA_AB.RData")
load("Arm-based Sim/df_direct_BNMA_AB.RData")
load("Arm-based Sim/df_overall_BNMA_AB.RData")

df_indirect_bias = df_indirect_bias[which(df_indirect_bias$pi_a==0.5),]
df_direct_bias = df_direct_bias[which(df_direct_bias$pi_a==0.5),]
df_BNMA_bias =  df_BNMA_bias[which(df_BNMA_bias$pi_a==0.5),]
df_indirect_new = df_indirect_new[which(df_indirect_new$pi_a==0.5),]
df_direct_new = df_direct_new[which(df_direct_new$pi_a==0.5),]
df_BNMA_new =  df_BNMA_new[which(df_BNMA_new$pi_a==0.5),]

a <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 6)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias[which(df_indirect_bias$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

b <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_bias[which(df_indirect_bias$k_ab==12),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


c <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Direct Evidence ($k_{BC}$ = 1, 2, 3, 6)"), color = TeX("True $OR_{BC}$"),  y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_bias[which(df_direct_bias$k_bc %in% c(1,2,3,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

d <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Direct Evidence ($k_{BC}$ = 2, 4, 6, 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_bias[which(df_direct_bias$k_bc %in% c(2,4,6,12)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


a1 <- df_BNMA_new %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 6)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_new[which(df_indirect_new$k_ab==6),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

b1 <- df_BNMA_new %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Indirect Evidence ($k_{AB}$ = $k_{AC}$ = 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_hline(linetype = "dashed", data = df_indirect_new[which(df_indirect_new$k_ab==12),], aes(yintercept = power, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


c1 <- df_BNMA_new %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Direct Evidence ($k_{BC}$ = 1, 2, 3, 6)"), color = TeX("True $OR_{BC}$"),  y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_new[which(df_direct_new$k_bc %in% c(1,2,3,6)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ ylim(0,1)
  

d1 <- df_BNMA_new %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = power, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Direct Evidence ($k_{BC}$ = 2, 4, 6, 12)"), color = TeX("True $OR_{BC}$"), y = "Power", x = "Number of Studies") + geom_line(linetype = "dotdash", data = df_direct_new[which(df_direct_new$k_bc %in% c(2,4,6,12)),], aes(y = power, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ ylim(0,1)


gridExtra::grid.arrange(a, a1, b, b1, c, c1, d, d1, nrow = 4)
```


# Bias in comparison: LARE - ABRE

## Absolute bias of overall evidence in comparison, pi_a = 0.1

```{r, fig.height=11, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias.RData")
load("NMA Power Sim/df_direct_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias3.RData")

df_indirect_summ = df_indirect_bias %>% group_by(pi_a, OR_bc, tau, k_ab, k_ac) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))

df_direct_summ = df_direct_bias %>% group_by(pi_a, OR_bc, tau, k_bc) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))

df_indirect_summ = df_indirect_summ[which(df_indirect_summ$pi_a==0.1),]
df_direct_summ = df_direct_summ[which(df_direct_summ$pi_a==0.1),]
df_BNMA_bias =  df_BNMA_bias[which(df_BNMA_bias$pi_a==0.1),]


load("Arm-based Sim/df_indirect_BNMA_AB_bias.RData")
load("Arm-based Sim/df_direct_BNMA_AB_bias.RData")
load("Arm-based Sim/df_overall_BNMA_AB_bias.RData")


df_indirect_new = df_indirect_new[which(df_indirect_new$pi_a==0.1),]
df_direct_new = df_direct_new[which(df_direct_new$pi_a==0.1),]
df_BNMA_new =  df_BNMA_new[which(df_BNMA_new$pi_a==0.1),]


a <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Overall vs. Only Indirect (k_ab = k_ac = 6)", color = "True OR_bc") + theme_bw() + geom_hline(linetype = "dashed", data = df_indirect_summ[which(df_indirect_summ$k_ab==6),], aes(yintercept = bias_avg, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

b <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Overall vs. Only Indirect (k_ab = k_ac = 12)", color = "True OR_bc") + theme_bw()  + geom_hline(linetype = "dashed", data = df_indirect_summ[which(df_indirect_summ$k_ab==12),], aes(yintercept = bias_avg, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0) 


c <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Overall vs. Only Direct (k_bc = 1, 2, 3, 6)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_summ[which(df_direct_summ$k_bc %in% c(1,2,3,6)),], aes(y = bias_avg, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

d <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Overall vs. Only Direct (k_bc = 2, 4, 6, 12)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_summ[which(df_direct_summ$k_bc %in% c(2,4,6,12)),], aes(y = bias_avg, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0)


a2 <- df_BNMA_new %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Overall vs. Only Indirect (k_ab = k_ac = 6)", color = "True OR_bc") + theme_bw() + geom_hline(linetype = "dashed", data = df_indirect_new[which(df_indirect_new$k_ab==6),], aes(yintercept = avg_bias_abs, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ geom_hline(yintercept = 0)
  

b2 <- df_BNMA_new %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Overall vs. Only Indirect (k_ab = k_ac = 12)", color = "True OR_bc") + theme_bw()  + geom_hline(linetype = "dashed", data = df_indirect_new[which(df_indirect_new$k_ab==12),], aes(yintercept = avg_bias_abs, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ geom_hline(yintercept = 0) + ylim(0, 0.2)


c2 <- df_BNMA_new %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Overall vs. Only Direct (k_bc = 1, 2, 3, 6)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_new[which(df_direct_new$k_bc %in% c(1,2,3,6)),], aes(y = avg_bias_abs, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

d2 <- df_BNMA_new %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Overall vs. Only Direct (k_bc = 2, 4, 6, 12)", color = "True OR_bc") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_new[which(df_direct_new$k_bc %in% c(2,4,6,12)),], aes(y = avg_bias_abs, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0)

gridExtra::grid.arrange(a, a2, b, b2, c, c2, d, d2, nrow = 4)
```



## Absolute bias of overall evidence in comparison, pi_a = 0.5

```{r, fig.height=11, fig.width=12}
load("NMA Power Sim/df_indirect_BNMA_bias.RData")
load("NMA Power Sim/df_direct_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias.RData")
load("NMA Power Sim/df_overall_BNMA_bias3.RData")

df_indirect_summ = df_indirect_bias %>% group_by(pi_a, OR_bc, tau, k_ab, k_ac) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))

df_direct_summ = df_direct_bias %>% group_by(pi_a, OR_bc, tau, k_bc) %>%
  summarise(power_prob = mean(power), rank_prob = mean(rank_correct),
            bias_avg = (mean(abs(point_est - point_true))))

df_indirect_summ = df_indirect_summ[which(df_indirect_summ$pi_a==0.5),]
df_direct_summ = df_direct_summ[which(df_direct_summ$pi_a==0.5),]
df_BNMA_bias =  df_BNMA_bias[which(df_BNMA_bias$pi_a==0.5),]


load("Arm-based Sim/df_indirect_BNMA_AB_bias.RData")
load("Arm-based Sim/df_direct_BNMA_AB_bias.RData")
load("Arm-based Sim/df_overall_BNMA_AB_bias.RData")


df_indirect_new = df_indirect_new[which(df_indirect_new$pi_a==0.5),]
df_direct_new = df_direct_new[which(df_direct_new$pi_a==0.5),]
df_BNMA_new =  df_BNMA_new[which(df_BNMA_new$pi_a==0.5),]


a <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Overall vs. Only Indirect (k_ab = k_ac = 6)", color = TeX("True $OR_{bc}$"), y = "Average Absolute Bias", x = "Number of Studies") + theme_bw() + geom_hline(linetype = "dashed", data = df_indirect_summ[which(df_indirect_summ$k_ab==6),], aes(yintercept = bias_avg, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)+ ylim(0, 0.25)
  

b <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Indirect ($K_{AB}$ = $K_{AC}$ = 12)"), color = TeX("True $OR_{bc}$"), y = "Average Absolute Bias", x = "Number of Studies") + theme_bw()  + geom_hline(linetype = "dashed", data = df_indirect_summ[which(df_indirect_summ$k_ab==12),], aes(yintercept = bias_avg, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0)  + ylim(0, 0.2)


c <- df_BNMA_bias %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "LARE: Overall vs. Only Direct (k_bc = 1, 2, 3, 6)", color = TeX("True $OR_{bc}$"), y = "Average Absolute Bias", x = "Number of Studies") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_summ[which(df_direct_summ$k_bc %in% c(1,2,3,6)),], aes(y = bias_avg, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

d <- df_BNMA_bias %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("LARE: Overall vs. Only Direct ($K_{bc}$ = 2, 4, 6, 12)"), color = TeX("True $OR_{bc}$"), y = "Average Absolute Bias", x = "Number of Studies") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_summ[which(df_direct_summ$k_bc %in% c(2,4,6,12)),], aes(y = bias_avg, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0)


a2 <- df_BNMA_new %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Overall vs. Only Indirect (k_ab = k_ac = 6)", color = TeX("True $OR_{bc}$"), y = "Average Absolute Bias", x = "Number of Studies") + theme_bw() + geom_hline(linetype = "dashed", data = df_indirect_new[which(df_indirect_new$k_ab==6),], aes(yintercept = avg_bias_abs, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1)))+ geom_hline(yintercept = 0)+ ylim(0, 0.25)
  

b2 <- df_BNMA_new %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Indirect ($K_{AB}$ = $K_{AC}$ = 12)"), color = TeX("True $OR_{bc}$"), y = "Average Absolute Bias", x = "Number of Studies") + theme_bw()  + geom_hline(linetype = "dashed", data = df_indirect_new[which(df_indirect_new$k_ab==12),], aes(yintercept = avg_bias_abs, color = factor(OR_bc))) + scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2)))+ geom_hline(yintercept = 0) + ylim(0, 0.2)


c2 <- df_BNMA_new %>% filter(k_ab == 6) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = "ABRE: Overall vs. Only Direct (k_bc = 1, 2, 3, 6)", color = TeX("True $OR_{bc}$"), y = "Average Absolute Bias", x = "Number of Studies") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_new[which(df_direct_new$k_bc %in% c(1,2,3,6)),], aes(y = avg_bias_abs, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(1, 6, 1), labels = as.character(seq(1, 6, 1))) + geom_hline(yintercept = 0)
  

d2 <- df_BNMA_new %>% filter(k_ab == 12) %>% 
  ggplot(aes(x = k_bc, y = avg_bias_abs, color = factor(OR_bc))) + geom_line(size = 1.2) +  geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("ABRE: Overall vs. Only Direct ($K_{bc}$ = 2, 4, 6, 12)"), color = TeX("True $OR_{bc}$"), y = "Average Absolute Bias", x = "Number of Studies") + theme_bw() + geom_line(linetype = "dotdash", data = df_direct_new[which(df_direct_new$k_bc %in% c(2,4,6,12)),], aes(y = avg_bias_abs, x = k_bc, color = factor(OR_bc)))+ scale_x_continuous(breaks = seq(2, 12, 2), labels = as.character(seq(2, 12, 2))) + geom_hline(yintercept = 0)

gridExtra::grid.arrange(a, a2, b, b2, c, c2, d, d2, nrow = 4)
```



```{r, fig.height=5.5, fig.width=12}
gridExtra::grid.arrange(b, b2, d, d2, nrow = 2)
```



# Part 4: Big vs Small Studies


# Total sample size 3000

```{r, fig.height=8, fig.width=16}
load("big_small/result_extreme_small3000/overall_result_big_small_new.RData")

gridExtra::grid.arrange(

overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) + 
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Power") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Probability of Correct Ranking") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = avg_bias_abs, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Average Absolute Bias") + theme_bw()
,

overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.01) %>% 
  ggplot(aes(x = n_study, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.01$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Power")+ theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.01) %>% 
  ggplot(aes(x = n_study, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.01$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Probability of Correct Ranking") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.01) %>% 
  ggplot(aes(x = n_study, y = avg_bias_abs, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.01$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Average Absolute Bias") + theme_bw()
,

overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Power")+ theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Probability of Correct Ranking") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = avg_bias_abs, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Average Absolute Bias") + theme_bw()
, nrow = 3)
```

```{r, fig.height=5.5, fig.width=16, eval = F, echo = F}
gridExtra::grid.arrange(
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) + geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Power") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Probability of Correct Ranking") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = avg_bias_abs, color = factor(OR_bc)))  + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Average Absolute Bias") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Power")+ theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Probability of Correct Ranking") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = avg_bias_abs, color = factor(OR_bc)))  + geom_line(size = 1.2) +geom_point(size = 2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Average Absolute Bias") + theme_bw()
, nrow = 2)
```





# Total sample size 30000

```{r, fig.height=8, fig.width=16}
load("big_small/result_extreme_small30000/overall_result_big_small_new.RData")

gridExtra::grid.arrange(

overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Power") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Probability of Correct Ranking") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.001) %>% 
  ggplot(aes(x = n_study, y = avg_bias_abs, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.001$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Average Absolute Bias") + theme_bw()
,

overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.01) %>% 
  ggplot(aes(x = n_study, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.01$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Power")+ theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.01) %>% 
  ggplot(aes(x = n_study, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.01$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Probability of Correct Ranking") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.01) %>% 
  ggplot(aes(x = n_study, y = avg_bias_abs, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.01$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Average Absolute Bias") + theme_bw()
,

overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = power, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau) + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Power")+ theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = rank_correct, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Probability of Correct Ranking") + theme_bw()
,
overall_result_big_small %>% mutate(n_study = k_ab + k_ac + k_bc) %>% 
  filter(pi_a == 0.1) %>% 
  ggplot(aes(x = n_study, y = avg_bias_abs, color = factor(OR_bc)))  + geom_line(size = 1.2) +
  facet_wrap(~tau)  + labs(title = TeX("Overall Evidence (K = 6,12,18,24), $pi_a = 0.1$"), color = TeX("True $OR_{bc}$"), x = "Number of Studies", y = "Average Absolute Bias") + theme_bw()
, nrow = 3)
```